%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Engineer, Offensive Security Research} % Job title
    {bKash Limited} % Organization
    {Dhaka, Bangladesh} % Location
    {Aug. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Conducted comprehensive vulnerability assessments regularly across web applications \& APIs, databases, servers and k8s clusters to identify and remediate security weaknesses.
        \item Partnered with cross-funtional teams to ensure the timely acknowledgement, triaging and remediation of critical findings.
        \item Translated vulnerability findings into prioritized actions, enabling systematic improvement of overall security resilience.
        \item Generated vulnerability status reports and executive summaries to communicate risk posture and remediation progress to higher \newline management.
        \item Collaborated with engineering, operations, and product teams to embed security measures during system and application development.
        \item Integrated and maintained SAST and DAST tools, ensuring continuous vulnerability scanning workflows.
        \item Drove the integration and maintenance of cloud and k8s security assessment tools to enhance security monitoring.
        \item Led proof-of-concept deployments of various security assessment tools, evaluating their effectiveness for enterprise adoption.
        \item Authored and maintained internal security documentation, including technical guidelines, best practices, and tool usage manuals.
        \item Established benchmarks for configuration audits, aligning with industry standards and compliance requirements.
        \item Maintained, upgraded and troubleshot tools such as RnD servers, vulnerability scanners, and other internal security platforms.
        \item Collaborated with vendors to resolve technical issues and coordinate feature upgrades.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Associate Software Engineer (Internship)} % Job title
    {Vivasoft Ltd} % Organization
    {Dhaka, Bangladesh} % Location
    {May. 2023 - Sept. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Collaborated within a team specializing in the development of an in-house product utilizing ASP.NET and .NET technologies.
        \item Conducted testing and debugging of the codebase to identify and resolve issues.
        \item Enhanced the overall stability and performance of the application.
        \item Contributed to the documentation of software architecture, system design, and technical specifications, facilitating knowledge transfer.
        \item Demonstrated adaptability and eagerness to learn new technologies and methodologies.
      \end{cvitems}
    }
%---------------------------------------------------------
  \vspace{10pt}
  \cventry
    {Web Developer (Part-Time)} % Job title
    {iMS Systems} % Organization
    {Remote} % Location
    {Apr. 2022 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Developed features for the backend of the application using NodeJS and MongoDB.
        \item Fixed bugs related to the backend and performed API testing using Postman.
        \item Conducted research and development for setting up a software testing infrastructure.
        \item Worked in a team with multiple developers and participated in daily standups.
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
